---
title: "Data Science and Solutions Technical Assessment"
author: "Thuy-Nhi Nguyen"
date: "1/7/2022"
output:
  word_document: default
  pdf_document: default
---


# Data Exploration

```{r}
addmargins(table(shots_data$team, shots_data$fgmade))
# team A made 105 shots out of 280 attempted
# team B made 115 shots out of 280 attempted
```

```{r}
two_point <- subset(shots_data, x <= 22 & x >= -22)
addmargins(table(two_point$team, two_point$fgmade))
# 105 out of 280 attempts were made for team A
# 115 out of 280 attempts were made for team B
95/256
108/255

(95 +(0.5 *8))/256
(108 +(0.5 *6))/255
```


```{r}
ncthree_point <- subset(shots_data, x > 23.73 & y > 7.8 | x < -23.75 & y < -7.8)
head(ncthree_point)
# none
```

```{r}
cthree_point <- subset(shots_data, x > 22 & y <= 7.8 | x < -22  & y >= -7.8)
addmargins(table(cthree_point$team, cthree_point$fgmade))
# 8 out of 20 attempts were made for team A
# 6 out of 23 attempts were made for team B
8/20
6/23

(8 +(0.5 *8))/20
(6 +(0.5 *6))/23
```

## Shot Distribution for each team

Shot distribution of Team A is 37.5%

Shot distribution of Team B is 42.1%


```{r}
105/280
115/280
```

## eFG% for each team

eFG% = (Field goals made + (0.5* 3 pts made) / Field goals attempted )



## Notes provided:

1) court_diagram.jpg
• An annotated diagram of the official NBA Court. All markers are measured in feet relative to the center of the hoop
• For all “Non Corner” 3’s (where Y > 7.8), the 3PT line is 23.75 ft from the center of the hoop
• For all “Corner” 3’s (where Y <= 7.8), the 3PT line is 22 feet from the court’s Y-axis at all points (note the definition of “Corner” 3 is not determined by the “break” in the arc)
2) shots_data.csv
• team: name of team (Team A, Team B)
• x: X-coordinate of the shot, measured in feet
• y: Y-coordinate of the shot, measured in feet
• fgmade: boolean value indicating the outcome of the shot (0=Miss, 1=Make)

Determine the shot zones (2PT, NC3, or C3) and calculate for each team the shot distribution and eFG%
Shot distribution: the percentage of team shots attempted within a zone
eFG%: the effective field goal percentage of team shots within a zone